\textbf{EECS 340: Assignment 3}

### 2020-02-21 assignment_3/article.tex
✨ Add Question 3 response.

>>>>

% \begin{tikzpicture}
%
% \matrix [matrix of nodes,
%          nodes = {draw,  minimum size = 2ex},
%          column sep=1ex, row sep=1ex,
%          row 1/.style={execute at begin cell= {|[label=\pgfmathparse{int(\the\pgfmatrixcurrentcolumn-1)}\pgfmathresult]|}}
%          ]
% {
% 9 & 2 & 4 & 4 & 5   \\
% 8 & 3 & 3 & 5 & 5   \\
% 7 & 4 & 2 & 7 & 5   \\
% 6 & 5 & 1 & 1 & 5   \\
% 5 & 6 & 0 & 2 & 5   \\
% };
% \end{tikzpicture}

\tikzset{
mymat/.style={
  matrix of math nodes,
  text height=2.5ex,
  text depth=0.75ex,
  text width=3.25ex,
  align=center,
  column sep=-\pgflinewidth
  },
mymats/.style={
  mymat,
  nodes={draw,fill=#1}
  }
}

\begin{tikzpicture}[>=latex]

\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (0,4.5)
(mat1)
{
1 & 2 & 3 & 4 & 5\\
> & > & > & > & ..\\
};

\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
at (0,3)
(mat2)
{
> & > & > & > & ..\\
};

\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
at (0,2)
(mat3)
{
> & > & > & > & ..\\
};

\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
at (0,1)
(mat4)
{
> & > & > & > & ..\\
};

\matrix[mymat,anchor=west,row 1/.style={nodes=draw}]
at (0,0)
(mat5)
{
> & > & > & > & ..\\
};

\matrix[mymat,right=of mat1,row 2/.style={nodes=draw}]
at (4.5,4.5)
(mat11)
{
1 & 2 & 3 & 4 & 5\\
> & > & > & > & ..\\
};

\matrix[mymat,right=of mat2,row 1/.style={nodes=draw}]
at (4.5,3)
(mat22)
{
> & > & > & > & ..\\
};

\matrix[mymat,right=of mat3,row 1/.style={nodes=draw}]
at (4.5,2)
(mat33)
{
> & > & > & > & ..\\
};

\matrix[mymat,right=of mat4,row 1/.style={nodes=draw}]
at (4.5,1)
(mat44)
{
> & > & > & > & ..\\
};

\matrix[mymat,right=of mat5,row 1/.style={nodes=draw}]
at (4.5,0)
(mat55)
{
> & > & > & > & ..\\
};

\matrix[mymat,right=of mat11,row 2/.style={nodes=draw}]
at (10,4.5)
(mat111)
{
1 & 2 & 3 & 4 & 5\\
M & X & X & > & ..\\
};

\matrix[mymat,right=of mat22,row 1/.style={nodes=draw}]
at (10,3)
(mat222)
{
X & X & > & > & ..\\
};

\matrix[mymat,right=of mat33,row 1/.style={nodes=draw}]
at (10,2)
(mat333)
{
X & > & > & > & ..\\
};

%
% \matrix[mymat,right=of mat44,row 1/.style={nodes=draw}]
% at (10,1)
% (mat444)
% {
% \geq & \geq & \geq & \geq & ..\\
% };
%
% \matrix[mymat,right=of mat55,row 1/.style={nodes=draw}]
% at (10,0)
% (mat555)
% {
% \geq & \geq & \geq & \geq & ..\\
% };

\node[above=20pt of mat1]
    (cella) {\textbf{Step 1:} $T(5)$};
\node[above=0pt of mat1]
    (cella) {$L[1] > L[2] > ... > L[5]$};

\node[above=20pt of mat11]
    (cella) {\textbf{Step 2:} $T(1)$};
\node[above=0pt of mat11]
    (cella) {$A[1] > B[1] > ... > E[1]$};

\node[above=20pt of mat111]
    (cella) {\textbf{Step 3:} $T(1)$};
\node[above=0pt of mat111]
    (cella) {Sort $A[2], A[3], B[1], B[2], C[1]$};

\node[left=0pt of mat1]
  (cella) {B};
\node[left=0pt of mat2]
  (cellb) {A};
\node[left=0pt of mat3]
  (cellb) {D};
\node[left=0pt of mat4]
  (cellb) {C};
\node[left=0pt of mat5]
  (cellb) {E};

\node[left=0pt of mat11]
(cella) {A};
\node[left=0pt of mat22]
(cellb) {B};
\node[left=0pt of mat33]
(cellb) {C};
\node[left=0pt of mat44]
(cellb) {D};
\node[left=0pt of mat55]
(cellb) {E};

\node[left=0pt of mat111]
(cella) {A};
\node[left=0pt of mat222]
(cellb) {B};
\node[left=0pt of mat333]
(cellb) {C};
% \node[left=0pt of mat444]
% (cellb) {D};
% \node[left=0pt of mat555]
% (cellb) {E};
\end{tikzpicture}\newline

\paragraph{Step 1: Divide\newline}
Divide the 25 elements into groups of 5, and sort each group internally. By that we may have five sorted lists, we denote them as $A, B, C, D, E$, with the relationship of

\begin{equation}
    L[1] > L[2] > L[3] > L[4] > L[5] \label{eq:divide_group}
\end{equation}

for $L \in \{A, B, C, D, E\}$. This step shall cost five experiments and thus carries a $T(5)$ runtime, assuming each experiment will take $T(1)$ to conduct.

\paragraph{Step 2: Sort front and find max candidate\newline}
Sort the 5 groups according to their first elements, in the demonstrated case, we have
\begin{equation}
    A[1] > B[1] > C[1] > D[1] > E[1] \label{eq:sort_front}
\end{equation}
This step shall cost one experiment and thus carries a $T(1)$ runtime.

According to \textit{Equation (\ref{eq:divide_group})} and \textit{Equation (\ref{eq:sort_front})}, we must have $A[1]$ being the material with maximum effectiveness amount all candidates. We may therefore add $A[1]$ into the result list.

\paragraph{Step 2: Find rest two candidates\newline}

According to \textit{Equation (\ref{eq:divide_group})} and \textit{Equation (\ref{eq:sort_front})}, we may safely claim the rest two candidates with top effetiveness must be among $A[2], A[3], B[1], B[2], C[1]$. Since it is known that $B[1] > C[1] > D[1] > E[1]$, we may discard $D[1], E[1]$ -- as there are always less effective in comparsion with $B[1], C[1]$ -- and therefore discarding group $D, E$, once again according to \textit{Equation (\ref{eq:divide_group})}.

However, we cannot determine the expicit relationship between  $A[2], A[3], B[1], B[2], C[1]$, thus we conduct another experiment and add the top two candidates to the result list. This step shall cost one experiment and thus carries a $T(1)$ runtime.

\paragraph{Total Runtime}

\begin{equation}
    T_{\text{total}} = T(5) + T(1) + T(1) = T(7) \label{eq:q4_runtime}
\end{equation}

As \textit{Equation (\ref{eq:q4_runtime})} is a sum of runtime cost from each step, we may conclude that our algoritm has a runtime of $T(4)$.
